Text Is All You Need

### 2023-05-11 docs/hes_final/presentation.qmd
fix typo

- Most contemporary work focuses on country or region-specific models. 
  + This introduces a “small-data problem” 
- We chose to persue a global model, a relatively new area of reseatch in this domain
  + This introduces a new problem of accounting for local conditions

>>>>

- Most contemporary work focuses on country or region-specific models. 
  + This introduces a “small-data problem” 
- We chose to persue a global model, a relatively new area of research in this domain
  + This introduces a new problem of accounting for local conditions
